Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-21 main.tex

 Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
 Since $\nabla u_{F_{m}|T_{j(m)}} = \nabla w_{m-1|T_{j(m)}}$,
 there exists a constant $c_{m} := w_{m-1|T_{j(m)}} - u_{F_{m}|T_{j(m)}}$.
 We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_{j(m)}} = w_{m-1|T_{j(m)}}$. 
 But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
 As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
 Moreover, 
 \begin{gather*}
    \| u'_{F_m} \|_{L^{p}(T_m)}

@@

    \| u_{F_m} \|_{L^{p}(T_m)}

@@

    \| c_{m} \|_{L^{p}(T_m)},
    \qquad 
    \| c_{m} \|_{L^{p}(T_m)}
    \| c_{m} \|_{L^{p}(T_{j(m)})},
    \| c_{m} \|_{L^{p}(T_{j(m)})}
    \| w_{m-1}\|_{L^{p}(T_{j(m)})} + \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
 \end{gather*}
 In particular,
    \| u_{F_m} \|_{L^{p}(T_m)}

@@

    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}

@@

@@

 We want to summarize the two integrals of $u_{F_m}$. 

@@

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \diam(T) \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where 
    \begin{align*}
        C_{\partial,p}
        \leq 
        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right) 
        .
    \end{align*}
    % \begin{align*}
    %     \| u \|_{L^{p}(T)}
    %     &
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla w \|_{\bfL^{p}(T)}
    %     +
    %     \| \gamma \|_{\bfL^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T)
    %     \| \nabla w \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} 
    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     .
    % \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The desired result follows. 
\end{proof}

@@

    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
    Let $\hat T$ be the reference simplex.
    % We fix affine homeomorphisms $\Phi : \hat T \rightarrow T_{j(m)}$ and $\Theta : \hat T \rightarrow T_{m+1}$,
    % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
    %
    We define $w'_{m+1} := w_{m} \circ \Xi \in W^{1,p}(T_{m+1})$,
    where $\Xi : T_{m+1} \rightarrow T_{j(m)}$ is the unique affine homeomorphism that leaves $F$ invariant. 
    %
    By construction, $w'_{m+1} \in W^{1,p}(T_{m+1})$ with 
    \begin{align*}
        \trace_F w_{m} = \trace_F w'_{m+1}
        .
    \end{align*}
    Suppose that $w''_{m+1} = u - w'_{m+1} \in W^{1,p}(T_{m+1})$.
    It satisfies 
    \begin{align*}
        \nabla w''_{m+1} = \nabla u - \nabla w'_{m+1}, 
        \quad 
        \trace_{F_{m}} w''_{m+1} = 0.
    \end{align*}
    The trace condition holds because 
    \begin{align*}
        \trace_{F_{m}}( \nabla u - \nabla w'_{m+1} ) 
        &= 
        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m+1}
        \\&= 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m+1}
        = 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m}
        = 
        0
        .
    \end{align*}
    Setting $w_{m+1} := w_{m}$ over $\Omega_{m}$ and $w_{m+1} := w'_{m+1} + w''_{m+1}$ over $T_{m+1}$, 
    we find 
    \begin{gather*}
        \nabla w_{m+1} = \nabla w'_{m+1} + \nabla w''_{m+1} = \nabla w'_{m+1} + \nabla u - \nabla w'_{m+1} = \nabla u,
        % \end{gather*}
        \\
        % \begin{gather*}
        \trace_{F_{m}} w_{m+1} = \trace_{F_{m}} w'_{m+1} = \trace_{F_{m}} w_{m}.
    \end{gather*}
    That means that $w_{m+1} \in W^{1,p}(\Omega_{m+1})$ with $\nabla w_{m+1} = \nabla u$ over $\Omega_{m+1}$. 
    Lemma~\ref{lemma:mixedbconsimplex} gives 
    \begin{align*}
        \| w''_{m+1} \|_{L^{p}(T_{m+1})} 
        &
        \leq 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u - \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}.
        \\&
        \leq 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u        \|_{L^{p}(T_{m+1})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
        .
    \end{align*}
    We use also employ Lemma~\ref{lemma:volumecomparison} to find 
    \begin{align*}
        \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}
        &\leq 
        |\det(\Dif \Xi  )|^{-\frac 1 p} 
        \| \Dif \Xi   \|
        \cdot 
        \| \nabla w_{m} \|_{L^{p}(T_{m})}
        \\&\leq 
        \kappa(\calT)^{1+\frac 1 p} 
        \sqrt{2n^{n+1}} 
        \cdot 
        \| \nabla w_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Putting this all together, 
    \begin{align*}
        &
        \| w_{m+1} \|_{L^{p}(T_{m+1})}
        \\&
        \leq  
        \| w'_{m+1} \|_{L^{p}(T_{m+1})}
        + 
        \| w''_{m+1} \|_{L^{p}(T_{m+1})}
        \\&
        \leq  
        \kappa(\calT) 
        \| w_{m} \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
        \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
        \\&
        \leq  
        \kappa(\calT) 
        \| w_{m} \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
        \kappa(\calT)^{1+\frac 1 p} 
        \sqrt{2n^{n+1}} 
        \cdot 
        \| \nabla w_{m} \|_{L^{p}(T_{m})} 
        \\&
        \leq  
        \kappa(\calT) 
        \| w_{m} \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
        \left( 1 + \kappa(\calT)^{1+\frac 1 p} \sqrt{2n^{n+1}} \right) 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        .
    \end{align*}
    % TODO: Finish the recursion 
    We will also use the bound.  
\end{proof}

>>>>

 Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
 Since $\nabla u_{F_{m}|T_{j(m)}} = \nabla w_{m-1|T_{j(m)}}$,
 there exists a constant $c_{m} := w_{m-1|T_{j(m)}} - u_{F_{m}|T_{j(m)}}$.
 We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_{j(m)}} = w_{m-1|T_{j(m)}}$. 
 But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
 As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
 Moreover, 
 \begin{gather*}
    \| u'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \qquad 
    \| c_{m} \|_{L^{p}(T_m)}
    \leq 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_{j(m)})},
    \\ 
    \| c_{m} \|_{L^{p}(T_{j(m)})}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_{j(m)})} + \| u_{F_{m}} \|_{L^{p}(T_{j(m)})} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_{j(m)})}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_{j(m)})^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_{j(m)})}
    .
 \end{align*}
 We want to summarize the two integrals of $u_{F_m}$.

 \newpage\color{red}
 We want 
    \| w_{m} \|_{L^{p}(T_m)}^{p}

@@

        1 

@@

        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}

@@

@@

        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}

@@

 In the special case $p=1$ and $p=\infty$,
    \| w_{m} \|_{L^{2}(T_m)}^{2}
        1 
        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    3
        ,
 \color{orange}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
 In the special case $p=1$ and $p=\infty$, 
    \| w_{m} \|_{L^{2}(T_m)}^{2}
        \| u_{F_m} \|_{L^{2}(T_m)}^{2}
        \| u_{F_{m}} \|_{L^{2}(T_{j(m)})}^{2}
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    3
        ,
 \color{JungleGreen}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
        3
    \right)^{p/q}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
    \\&
        3
    \right)^{p/q}
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
 In the special case $p=1$ and $p=\infty$, ????
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})}^{1}
        \| w_{m-1}\|_{L^{1}(T_{j(m)})}^{1}
    \| w_{m} \|_{L^{2}(T_m)}^{2}
    3
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    3
        ,
 \color{MidnightBlue}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
    \\&
        \frac{ \vol(T_m)^{\frac q p} }{ \vol(T_{j(m)})^{\frac q p} }
    \right)^{p/q}
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{p}(T_m \cup T_{j(m)})}^{p}
        \| w_{m-1}\|_{L^{p}(T_{j(m)})}^{p}
 In the special case $p=1$ and $p=\infty$, ????
    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{1}(T_m \cup T_{j(m)})} 
    \| w_{m} \|_{L^{2}(T_m)}^{2}
        \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_{j(m)}) } \right)
        \| u_{F_{m}} \|_{L^{2}(T_m \cup T_{j(m)})}^{2}
        \| w_{m-1}\|_{L^{2}(T_{j(m)})}^{2}
    3
        ,
 \color{black}

@@

\begin{lemma}\label{lemma:mixedbconsimplex}
    Let $T$ be an $n$-simplex and with a face $F$. 
    If $u \in W^{1,p}(T)$ such that $\trace_{F} u = 0$, then 
    \begin{align*}
        \| u \|_{L^{p}(T)}
        &
        \leq 
        C_{{\rm PF},T,F,p} \diam(T) \| \nabla u \|_{L^{p}(T)}
    \end{align*}
    where $C_{\partial,p} > 0$ is a constant such that 
    \begin{align*}
        C_{\partial,p}
        \leq 
        \left( C_{{\rm PF},T,F,p} + \left( C_{{\rm PF},T,F,p}^{p} + p \cdot C_{{\rm PF},T,F,p}^{p-1} \right)^{\frac 1 p} \right),  
        \quad 
        C_{\partial,p}
        \leq 
        2^{\frac n p}
        .
    \end{align*}
    % \begin{align*}
    %     \| u \|_{L^{p}(T)}
    %     &
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla w \|_{\bfL^{p}(T)}
    %     +
    %     \| \gamma \|_{\bfL^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} \diam(T)
    %     \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T)
    %     \| \nabla w \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     C_{?} 
    %     \diam(T) \| \nabla u \|_{\bfL^{p}(T)}
    %     +
    %     \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p}
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     \\&
    %     \leq 
    %     \left( C_{?} + \left( C_{?}^{p} + p \cdot C_{?}^{p-1} \right)^{\frac 1 p} \right) 
    %     \diam(T) \| \nabla u \|_{L^{p}(T)}
    %     .
    % \end{align*}
\end{lemma}
\begin{proof}
    There exists $w \in W^{1,p}(T)$ with $\nabla w = \nabla u$ and 
    \[
        \| w \|_{L^{p}(T)}
        \leq 
        C_{{\rm PF},T,p} 
        \| \nabla w \|_{\bfL^{p}(T)}
        .
    \]
    Then $w-u$ is constant, and thus $\gamma := \trace_{F} (w-u) = \trace_{F} w$. 
    We use that 
    \[
        \| \gamma \|_{L^{p}(T)}
        =
        \gamma \vol(T)^\frac{1}{p}
        =
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \cdot 
        \gamma 
        \vol(F)^\frac{1}{p}
        \leq 
        \left( \frac{ \vol(T) }{ \vol(F) } \right)^\frac{1}{p}
        \| \gamma \|_{L^{p}(F)}
        .
    \]
    Using a trace inequality~\cite[Lemma~2.8]{veeser2012poincare} when $1 \leq p < \infty$, we find 
    \begin{align*}
        \| \gamma \|_{L^{p}(F)}^{p}
        &
        \leq 
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p}
        +
        p
        \cdot 
        \diam(T)
        \frac{ \vol(F) }{ \vol(T) }
        \| w \|_{L^{p}(T)}^{p-1}
        \| \nabla w \|_{L^{p}(T)}
        \\&
        \leq 
        \left( C_{{\rm PF},T,p}^{p} + p \cdot C_{{\rm PF},T,p}^{p-1} \right) 
        \diam(T)^{p}
        \left( \frac{ \vol(F) }{ \vol(T) } \right)
        \| \nabla w \|_{L^{p}(T)}^{p}
        .
    \end{align*}
    Recall that $u = w - \gamma$. The first inequality follows.

    There exists $\Psi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F$.
    We let $\hat u := u \circ \Psi$ and define $\hat g \in \bfL^p(\hat T)$ via $\hat g := \nabla ( u \circ \Psi )$. 
    Then $\nabla \hat u = \hat g$. 
    % 
    Let $\hat U$ be the unit ball of the $\ell^1$ metric, which contains $\hat T$.
    We let $\tilde u$ be the extension of $\hat u$ onto $\hat U$ by reflection across the coordiante axes.
    We define $\tilde g = \nabla \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\hat U$ by reflection across the coordinate axes. 
    By construction $\tilde u$ vanishes at the boundary of $\hat U$, and thus Friedrichs inequality satisfies 
    \begin{gather*}
        \| \tilde u \|_{L^{p}(\hat U)} 
        \leq 
        2 
        \| \tilde g \|_{\bfL^{p}(\hat U)}
        .
    \end{gather*}
    In addition to that, 
    \begin{gather*}
        \| u \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Dif \Psi)|^{\frac 1 p} 
        \| \hat u \|_{L^{p}(\hat T)}
        \leq 
        |\det(\Dif \Psi)|^{\frac 1 p} 
        \| \tilde u \|_{L^{p}(\hat U)}
        ,
        \\
        \| \tilde g \|_{\bfL^{p}(\hat U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{\bfL^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Dif \Psi_1)|^{-\frac 1 p} \| \Dif \Psi \| \cdot 
        \| \nabla u \|_{\bfL^{p}(T)}
        .
    \end{gather*}
    The second inequality follows.
\end{proof}

@@

    By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j(m)}$. 
    Let $\hat T$ be the reference simplex.
    % We fix affine homeomorphisms $\Phi : \hat T \rightarrow T_{j(m)}$ and $\Theta : \hat T \rightarrow T_{m+1}$,
    % each of which maps the convex closure of $v_0, \dots, v_{n-1}$ onto the common face $F_{m}$.
    %
    We define $w'_{m+1} := w_{m} \circ \Xi \in W^{1,p}(T_{m+1})$,
    where $\Xi : T_{m+1} \rightarrow T_{j(m)}$ is the unique affine homeomorphism that leaves $F$ invariant. 
    %
    By construction, $w'_{m+1} \in W^{1,p}(T_{m+1})$ with 
    \begin{align*}
        \trace_F w_{m} = \trace_F w'_{m+1}
        .
    \end{align*}
    Suppose that $w''_{m+1} = u - w'_{m+1} \in W^{1,p}(T_{m+1})$.
    It satisfies 
    \begin{align*}
        \nabla w''_{m+1} = \nabla u - \nabla w'_{m+1}, 
        \quad 
        \trace_{F_{m}} w''_{m+1} = 0.
    \end{align*}
    The trace condition holds because 
    \begin{align*}
        \trace_{F_{m}}( \nabla u - \nabla w'_{m+1} ) 
        &= 
        \trace_{F_{m}} \nabla u - \trace_{F_{m}} \nabla w'_{m+1}
        \\&= 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w'_{m+1}
        = 
        \nabla \trace_{F_{m}} u - \nabla \trace_{F_{m}} w_{m}
        = 
        0
        .
    \end{align*}
    Setting $w_{m+1} := w_{m}$ over $\Omega_{m}$ and $w_{m+1} := w'_{m+1} + w''_{m+1}$ over $T_{m+1}$, 
    we find 
    \begin{gather*}
        \nabla w_{m+1} = \nabla w'_{m+1} + \nabla w''_{m+1} = \nabla w'_{m+1} + \nabla u - \nabla w'_{m+1} = \nabla u,
        % \end{gather*}
        \\
        % \begin{gather*}
        \trace_{F_{m}} w_{m+1} = \trace_{F_{m}} w'_{m+1} = \trace_{F_{m}} w_{m}.
    \end{gather*}
    That means that $w_{m+1} \in W^{1,p}(\Omega_{m+1})$ with $\nabla w_{m+1} = \nabla u$ over $\Omega_{m+1}$. 
    Lemma~\ref{lemma:mixedbconsimplex} gives 
    \begin{align*}
        \| w''_{m+1} \|_{L^{p}(T_{m+1})} 
        &
        \leq 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u - \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}.
        \\&
        \leq 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla u        \|_{L^{p}(T_{m+1})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
        .
    \end{align*}
    We also employ Lemma~\ref{lemma:volumecomparison} to find 
    \begin{align*}
        \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})}
        &\leq 
        |\det(\Dif \Xi  )|^{-\frac 1 p} 
        \| \Dif \Xi   \|
        \cdot 
        \| \nabla w_{m} \|_{L^{p}(T_{m})}
        \leq 
        \kappa(\calT)^{\frac 1 p} \xi(\calT)
        \cdot 
        \| \nabla w_{m} \|_{L^{p}(T_{m})}
        .
    \end{align*}
    Putting this all together, 
    \begin{align*}
        &
        \| w_{m+1} \|_{L^{p}(T_{m+1})}
        \\&
        \leq  
        \| w'_{m+1} \|_{L^{p}(T_{m+1})}
        + 
        \| w''_{m+1} \|_{L^{p}(T_{m+1})}
        \\&
        \leq  
        \kappa(\calT)^{\frac 1 p} 
        \| w_{m} \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T,F,p} \diam(T_{m+1}) 
        \left( 
            \| \nabla u \|_{L^{p}(T_{m+1})} 
            + 
            \| \nabla w'_{m+1} \|_{L^{p}(T_{m+1})} 
        \right) 
        \\&
        \leq  
        \kappa(\calT)^{\frac 1 p} 
        \| w_{m} \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T,F,p} 
        \left( 1 + \kappa(\calT)^{\frac 1 p} \xi(\calT) \right) 
        \diam(T_{m+1}) 
        \| \nabla u \|_{L^{p}(T_{m+1})} 
        .
    \end{align*}
    % TODO: Finish the recursion 
\end{proof}
